### 2017-03-20 thesis/thesis.tex
finished rough draft of the result summary section in discussion - tmp commit
Started on limitations section - tmp commit
tmp commit
Finished discussion, now edit everything - tmp commit
Changed all the data set names and removed "'s" - tmp commit
Finished draft appendix A - tmp commit
Divided the appendix file into two - tmp commit
Need to add linear model prediction scatter plots - tmp commit
Added all of the extra results in appendix2; clean up the titles - tmp commit
Draft thesis completed; now edit the whole thing - tmp commit
Edited Intro
Finished editing results1

% Preamble:
\usepackage[T1]{fontenc}                            % package for specifying output font encoding
\usepackage[acronym]{glossaries}                    % package for making glossaries
\usepackage[flushleft]{threeparttable}              % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption} % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}        % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                           % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}          % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                          % package for making appendices
\usepackage[utf8]{inputenc}                         % package for specifying input font encoding
\usepackage{chngcntr}                               % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                               % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                               % package for Times New Roman font
\usepackage{natbib}                                 % package for reference management
\usepackage{setspace}                               % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                        % package for making colours
\usepackage{booktabs}                               % package for better looking tables
\usepackage{longtable}                              % package for tables that span multiple pages
\usepackage{siunitx}                                % package for scientific notations and units
\usepackage{etoolbox}                               % package to 'robustify' \bfseries

@@

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
\includeonly{{./methods/methods},{./results/results},{./results/results2},{./discussion/discussion},{./misc/appendix}}
% \includeonly{{./results/results},{./results/results2},{./misc/appendix}}
% \includeonly{{./results/results},{./results/results2},{./discussion/discussion},{./misc/appendix}}

@@

@@

% Print out the bibliography:
\bibliography{./MSc,./MSc2}

>>>>

% Preamble:
\usepackage[T1]{fontenc}                            % package for specifying output font encoding
\usepackage[acronym]{glossaries}                    % package for making glossaries
\usepackage[flushleft]{threeparttablex}              % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption} % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}        % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                           % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}          % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                          % package for making appendices
\usepackage[utf8]{inputenc}                         % package for specifying input font encoding
\usepackage{chngcntr}                               % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                               % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                               % package for Times New Roman font
\usepackage{natbib}                                 % package for reference management
\usepackage{setspace}                               % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                        % package for making colours
\usepackage{booktabs}                               % package for better looking tables
\usepackage{longtable}                              % package for tables that span multiple pages
\usepackage{siunitx}                                % package for scientific notations and units
\usepackage{etoolbox}                               % package to 'robustify' \bfseries

@@

% Set up continuous figures:
\DeclareCaptionFormat{cont}{#1 (cont.)\par}

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
% \includeonly{{./intro/intro}}
\includeonly{{./methods/methods},{./results/results2},{./misc/appendix2}}
% \includeonly{{./results/results}}
% \includeonly{{./results/results2}}
% \includeonly{{./discussion/discussion}}
% \includeonly{{./misc/appendix}}
% \includeonly{{./misc/appendix2}}

\defcitealias{TCGA}{NCI and NHGRI, 2016}
\defcitealias{ICGC}{ICGC, 2016}
\defcitealias{GEO}{NCBI, 2016}

@@

\include{./misc/appendix2}

@@

% Print out the bibliography:
\bibliography{./MSc,./msc2,./msc3}
